Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-11-27 Paper/main.tex
Updating paper latex files

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
  Shashank Yellapantula\footnote{SOME JOB TITLE, AIAA Member}
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

\author{Nathaniel B. deVelder\footnote{Postdoctoral appointee, AIAA member} and
  Alan S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies Department, AIAA member}}
\affil{Sandia National Laboratories, Albuquerque, NM 87185}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$\alpha$  & Wind shear exponent  \\
$L$       & Obukhov length scale \\
$u_\tau$   & Friction velocity    \\
$TI$      & Turbulence intensity 
\end{longtable*}}

\section{Introduction}
\fxnote{This is the introduction from the abstract.  Update with real
  introduction.}

\lettrine{P}{ut} the introduction here.

The planned installation of several offshore wind energy plants in the
United States has highlighted the need to properly understand the wind
resource and atmospheric characteristics of the US Atlantic Coast.
Several atmospheric phenomena particular to this region, such as
coastal low-level jets or seasonal Nor’easters, have the potential to
substantially impact the operation and power production of offshore
wind plants.  Of particular interest to the current study is the
atmospheric stability of the marine boundary layer in the Northeastern
US.

@@

@@

\section*{Acknowledgments}
\fxnote{Acknowledge Matt for work on BC}

@@

\fxnote{ADD ANY NREL ACKNOWLEDGEMENTS NECESSARY HERE}

% \bibliography{sample}
\bibliography{references}

>>>>

\author{
  Shreyas Ananthan\footnote{SOME JOB TITLE, AIAA Member},
  Michael J. Brazell\footnote{Researcher III, High-Performance Algorithms and Complex Fluids, AIAA Member},
  Ganesh Vijayakumar\footnote{Researcher III, Mechanical Engineering, AIAA Member}, and
}
\affil{National Renewable Energy Laboratory, Golden CO 80401}

\author{Nathaniel B. deVelder\footnote{Postdoctoral appointee, Wind
    Energy Technologies Department, AIAA member} and Alan
  S. Hsieh.\footnote{Postdoctoral appointee, Wind Energy Technologies
    Department, AIAA member}} \affil{Sandia National Laboratories,
  Albuquerque, NM 87185}

@@

{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable*}{@{}l @{\quad=\quad} l@{}}
$\alpha$  & Wind shear exponent  \\
$L$       & Obukhov length scale \\
$u_\tau$   & Friction velocity    \\
$R_{ij}$   & Two point correlation tensor \\
$TI$      & Turbulence intensity 
\end{longtable*}}

\section{Introduction}
\fxnote{Update this introduction.}

\lettrine{T}he planned installation of several offshore wind energy
plants in the United States has highlighted the need to properly
understand the wind resource and atmospheric characteristics of the US
Atlantic Coast.  Several atmospheric phenomena particular to this
region, such as coastal low-level jets or seasonal Nor’easters, have
the potential to substantially impact the operation and power
production of offshore wind plants.  Of particular interest to the
current study is the atmospheric stability of the marine boundary
layer in the Northeastern US.

@@

\fxnote{Mention study by \cite{wurps2020grid}.}

@@

\section*{Acknowledgments}
\fxnote{Acknowledge Matt for work on BC} \\
\fxnote{Acknowledge Shashank for work on BC}

@@

This work was authored in part by the National Renewable Energy
Laboratory, operated by Alliance for Sustainable Energy, LLC, for the
U.S. Department of Energy (DOE) under Contract No. DE-AC36-
08GO28308. M. Brazell was partially funded by the Exascale Computing
Project (17-SC-20-SC), a collaborative effort of two DOE organizations
(Office of Science and the National Nuclear Security Administration).

A portion of the research was performed using computational
resources sponsored by the Department of Energy's Office of Energy
Efficiency and Renewable Energy and located at the National Renewable
Energy Laboratory.

\bibliography{references}

### 2020-11-27 Paper/methodology.tex
Update paper stuff
Updating paper latex files

Write something about Cape Wind measurements from \cite{archer2016predominance}.

\subsection{LES Codes}
Provide a general description of the LES codes that we use.

\subsubsection{Nalu-Wind}
Describe Nalu-Wind

@@

\subsubsection{Simulation workflow}
Describe the process to hit target conditions.

>>>>

Following the work of Cheung et al \cite{cheung2020large}, we use
measurements of the offshore coastal marine boundary layer, collected
by the Cape Wind meteorological tower in Nantucket Sound, as the basis
for this computational study.  The Cape Wind platform collected wind
measurements at 20m, 41m, and 60m above the mean water level, along
with temperature and barometric measurements from the years 2003-2011.
From the observations, Archer et al.\cite{archer2016predominance}
found that the marine boundary layer is predominantly unstable, with
61\% of conditions classified as unstable, versus 21\% neutral and
18\% stable.  The stratification of the marine boundary layer, as
determined by the Obukhov length, also had a large impact on the wind
speed profile, with flatter, non-logarithmic profiles seen during
unstable conditions.

From the measured distribution of atmospheric stabilities, turbulent
kinetic energies (TKE), and wind speeds from the Cape Wind platform, a
specific set of conditions were chosen as targets for this
computational study.  A summary of the conditions for all stability
classes is given table \ref{tab:CapeWindMeasurements}. In this work we
focus on the three stable atmospheric conditions at wind speeds of
5m/s, 10m/s, and 15m/s, while the neutral and unstable conditions
where studied in previous work \cite{cheung2020large}.

To maintain consistency with the measured data, the turbulence
intensity (TI) is calculated using the TKE as
\begin{equation}
  \textrm{TI} =
  \frac{\sqrt{\frac{2}{3}\times\textrm{TKE}}}{\overline{U}_{horiz}} =
  \frac{\sqrt{\frac{1}{3}\left( \overline{u'u' + v'v' + w'w'}
      \right)}}{\overline{U}_{horiz}}
\end{equation}
The averaged wind speeds were enforced at the measurement height of
20m, and the wind directions...

\begin{table}
\caption{\label{tab:CapeWindMeasurements} Measured conditions at Cape
  Wind.  The stable atmospheric conditions used in this study are
  highlighted in bold below.} \centering
\begin{tabular}{cccc}
  \hline
  Stability    & Wind speed [m/s] & Wind dir [deg] & Turbulence intensity \\
  \hline
  Neutral      & 5                & 225            & 0.055           \\
  Neutral      & 10               & 225            & 0.055           \\
  Neutral      & 15               & 225            & 0.065           \\
  Unstable     & 5                & 315            & 0.080           \\
  Unstable     & 10               & 315            & 0.075           \\
  Unstable     & 15               & 315            & 0.090           \\
  \bf{Stable}  & \bf{5}           & \bf{225}       & \bf{0.045}      \\
  \bf{Stable}  & \bf{10}          & \bf{225}       & \bf{0.050}      \\
  \bf{Stable}  & \bf{15}          & \bf{225}       & \bf{0.060}      \\
\hline
\end{tabular}
\end{table}

\subsection{Computational methodlogy}
Provide a general description of the LES codes that we use.

\subsection{LES formulation}

\subsubsection{Governing equations}

\subsubsection{Nalu-Wind}
\fxnote{Shreyas write this part}\\
Describe Nalu-Wind

@@

\begin{table}
\caption{\label{tab:Computational parameters} LES parameters for stable conditions}
\centering
\begin{tabular}{cccc}
  \hline
  Stability    & Wind speed  & Surface roughness $z_0$ & Temperature gradient \\
  \hline
  Stable       & 5  m/s           & 0.0005 m       & -0.32 K/hr      \\
  Stable       & 10 m/s           & 0.0005 m       & -1.40 K/hr      \\
  Stable       & 15 m/s           & 0.0005 m       & -1.50 K/hr      \\
\hline
\end{tabular}
\end{table}

\subsubsection{Simulation workflow}
\fxnote{Lawrence write this part}\\
Describe the process to hit target conditions.

### 2020-11-27 Paper/results.tex
Updating paper latex files

\subsection{ABL integrated quantities}
Describe integrated quantities

\subsection{Horizontally averaged profiles}

\subsection{Wind spectra and turbulence statistics}

>>>>

\subsection{Domain and grid resolution study}

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:GridStudySetup} The setup for the grid resolution study} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & dy [m] & dz [m] \\
  \hline
  Nalu-wind coarse  &  10.0  & 10.0   & 2.5   \\
  Nalu-wind medium  &   5.0  &  5.0   & 2.5   \\
  Nalu-wind fine    &   2.5  &  2.5   & 2.5   \\
  AMR-wind fine     &   2.5  &  2.5   & 2.5   \\
\hline
\end{tabular}
\end{table}

The maximum resolvable frequency on a mesh with grid size $\Delta$ and
average horizontal wind speed $\bar{U}_{horiz}$ can be estimated as
\begin{equation}
  \label{eq:fmax}
  f_{max} = \frac{0.6\bar{U}_{horiz}}{N\Delta}.
\end{equation}
Here, equation \ref{eq:fmax} assumes that the turbulent eddies convect
with a velocity of $0.6\bar{U}_{horiz}$ and $N=8$ is chosen for the
purposes of this study.  Due to the alignment of the flow with the
mesh directions, the grid size $\Delta = \sqrt{2}\cdot \textrm{dx}$.

The wind spectra
\begin{equation}
  \int_0^\infty S_i(f) \textrm{d}f = \sigma_i^2
\end{equation}

%%%%%%%%%%% Grid resolution spectra figure %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Spectra.ipynb
\begin{figure}[hbt!]
  \label{fig:GridStudySpectra}
  \centering
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Su.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sv.png}
  \includegraphics[width=2.0in]{figures/GridStudy_Spectra_Sw.png}
  \caption{Calculation of the wind spectra $S_i$ for LES of stable
    5m/s case with different resolutions.  The gray vertical lines
    correspond to the maximum resolvable frequency according to
    equation (\ref{eq:fmax}). }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The two-point correlation tensor defined as
\begin{equation}
  \label{eq:Rij}
  R_{ij}({\mathbf x},\boldsymbol{\xi}) = 
  \frac{\overline{ {u'_i(\mathbf{x}, t) u'_j(\mathbf{x}+\boldsymbol{\xi},t)} }}
       { \sqrt{\overline{ u'^2_i }} \sqrt{\overline{ u'^2_j}} }
\end{equation}
where the velocity fluctuations $u'_i$ are defined as 
\begin{equation}
  u'_i(\mathbf{x},t) = u_i(\mathbf{x},t) - \overline{ u_i(\mathbf{x},t) }
\end{equation}

The horizontally averaged correlation coefficient $\langle
R_{ij}(\boldsymbol{\xi})\rangle$ is computed from
$R_{ij}(\mathbf{x},\boldsymbol{\xi})$ by sampling over ...

%%%%%%%%%%% Grid resolution correlation figure %%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/GridStudy/GridStudy_Rij.ipynb
\begin{figure}[hbt!]
  \label{fig:GridStudyRij}
  \centering
  \includegraphics[width=3in]{figures/GridStudy_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/GridStudy_Rij_Lateral.png}
  \caption{Calculation of the averaged longitudinal and lateral
    $R_{ij}(\xi)$ coefficient at $z$=20m for LES of stable 5m/s case
    with different resolutions.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The turbulent integral lengthscale can be calculated from $\langle
R_{ij}(\xi) \rangle$ via
\begin{equation}
  L = \int_0^\infty \langle R_{ij}(\xi) \rangle \: {\textrm d}\xi
\end{equation}

%%%%%%%%%%%%%%% GRID STUDY: INTEGRAL LENGTH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:GridStudyLscale} The calculated turbulent integral
  lengthscale for each of the grid resolutions} \centering
\begin{tabular}{ccccc}
  \hline
  Case              & dx [m] & Longitudinal L [m] & Lateral L [m] \\
  \hline
  Nalu-wind coarse  &  10.0  & 36.433999          & 0.0        \\
  Nalu-wind medium  &   5.0  & 21.485711          & 4.519247   \\
  AMR-wind fine     &   2.5  & 27.689340          & 9.332672   \\
\hline
\end{tabular}
\end{table}

\subsection{Comparison of AMR-Wind vs Nalu-Wind}

\subsection{ABL Physics}

\subsubsection{ABL integrated quantities}
Describe integrated quantities

\subsubsection{Horizontally averaged profiles}

\subsubsection{Wind spectra and turbulence statistics}

The Kaimal model for spectra \cite{kaimal1973turbulence, cheynet2017spectral}
\begin{equation}
  \label{eq:kaimal}
  \frac{fS_i}{u_\tau^2} = \frac{a_i(fz/\bar{U})}{\left(1+b_i(fz/\bar{U})^{\alpha_i}\right)^{\beta_i}}
\end{equation}

%%%%%%%%%%%%%%% KAIMAL MODEL PARAMETERS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{\label{tab:KaimalParameters} Parameters for Kaimal model}
\centering
\begin{tabular}{ccccc}
  \hline
  Velocity & $a_i$ & $b_i$ & $\alpha_i$  & $\beta_i$ \\
  \hline
  $u$      & 105.0 & 33.0  & 1           & 5/3  \\
  $v$      &  17.0 &  9.5  & 1           & 5/3  \\
  $w$      &   2.1 &  5.3  & 5/3         &   1  \\
\hline
\end{tabular}
\end{table}

\subsubsection{Comparison with neutral and unstable conditions}

%%%%%%%%%%% All stability correlation figure %%%%%%%%%%%%%%%%%%%%
% created in Postprocessing/ABLLength/CompareAll_ABL_Lengthscales.ipynb 
\begin{figure}[hbt!]
  \label{fig:AllStabilityRij}
  \centering
  \includegraphics[width=3in]{figures/AllStability_Rij_Longitudinal.png}
  \includegraphics[width=3in]{figures/AllStability_Rij_Lateral.png}
  \caption{Calculation of the averaged longitudinal and lateral
    $R_{ij}(\xi)$ coefficient at $z$=20m for all ABL stability cases.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
